\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{%
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Rajvendra Rahi} \\
  \small +91 8109204371 $|$ \href{mailto:rajvendrarahi126@gmail.com}{rajvendrarahi126@gmail.com} $|$ 
  \href{https://linkedin.com/in/rajvendra-rahi}{linkedin.com/in/rajvendra-rahi} $|$ 
  \href{https://github.com/Rajvendra-Rahi}{github.com/Rajvendra-Rahi}
\end{center}

\section*{Summary}
Data scientist with expertise in machine learning and statistical analysis. Proficient in Python, SQL, and data visualization tools like Power BI and Tableau. Experienced in developing and deploying machine learning models to derive actionable insights and drive data-informed decision-making. Eager to apply technical skills and analytical abilities to solve complex problems and contribute to a data-driven organization.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: Python, SQL, R (Basic)}
  \resumeItem{\textbf{Machine Learning}: Scikit-learn, TensorFlow, Deep Learning, NLP}
  \resumeItem{\textbf{Data Visualization}: Power BI, Tableau, Seaborn, Matplotlib, Word Cloud}
  \resumeItem{\textbf{Data Management}: Excel, Power Query Editor, DAX, PostgreSQL, MySQL}
  \resumeItem{\textbf{Statistical Analysis}: Statistical Techniques, Regression, Segmentation}
  \resumeItem{\textbf{Tools}: Git, Jupyter Notebook, VS Code}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
  \resumeSubheading
      {Artificial Neural Network From Scratch}{Feb 2025}
      {AlmaBetter/IITVerified}{Python, Numpy, Matplotlib}
      \resumeSubHeadingList
          \resumeItem{\textbullet Created a custom neural network from scratch using Python and NumPy, achieving 99.3\% accuracy on a spiral dataset.}
          \resumeItem{\textbullet Implemented forward and back propagation and developed a custom cross-entropy loss function.}
          \resumeItem{\textbullet Developed a small framework like tensor flow using oops in which deep fully connected neural networks can be created.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Credit Score Prediction}{Oct 2024}
      {AlmaBetter/IITVerified}{Python, Scikit-learn, Logistic Regression}
      \resumeSubHeadingList
          \resumeItem{\textbullet Applied data cleaning, visualization, and feature extraction techniques to improve the accuracy of predicting user credit scores by 15\%.}
          \resumeItem{\textbullet Implemented machine learning models such as Logistic Regression and Random Forest, optimizing hyper parameters to enhance model performance and stability.}
      \resumeSubHeadingListEnd
   \resumeSubheading
      {Book Recondamation System}{Feb 2024}
      {AlmaBetter Certified Project}{Python, Cosine Similarity}
      \resumeSubHeadingList
          \resumeItem{\textbullet Developed a high-accuracy Book Recommendation System using Python, achieving a 90\% accuracy rate in book recommendations by implementing cosine similarity.}
          \resumeItem{\textbullet Utilized data processing and machine learning libraries, including Pandas, NumPy, and scikit-learn, to efficiently preprocess large datasets and build recommendation models.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Sky Analytics Airline and Airport Operations Analysis}{Oct 2024}
      {AlmaBetter Verified Project}{MS Excel, Pivot Tables, Power Query}
      \resumeSubHeadingList
          \resumeItem{\textbullet Leveraged advanced Excel techniques for an in-depth analysis of approximately 70,000 flight records, examining delays, cancellations, airline performance, and airport traffic.}
          \resumeItem{\textbullet Developed functional dashboards that revealed key insights, including that 3.91\% flights got canceled, while 49.05\% got delayed.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
      {Data Scientist Trainee}{Jan 2024 -- Present}
      {AlmaBetter}{Bengaluru (Remote)}
      \resumeSubHeadingList
          \resumeItem{\textbullet Trained and optimized machine learning models utilizing algorithms such as Linear Regression, KNN, Decision Trees, and XGBoost; achieved classification accuracy of 87\%.}
          \resumeItem{\textbullet Cultivated strong collaboration skills through participation in multidisciplinary projects, resulting in a 15\% increase in team output and the successful completion.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {Barkatullah University (BUIT)}{}
      {B.Tech in Computer Science Engineering}{2020 -- 2024}
      \resumeSubHeadingList
          \resumeItem{CGPA: 7.2}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\textbullet Advanced Certification in Full Stack Data Science \& AI - Indian Institute of Technology (IIT) (Expected Dec 2024)}
\resumeSubHeadingListEnd

\end{document}