\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\,\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Trivendra Rahi}} & Email: \href{mailto:trivendra.rahi05@gmail.com}{trivendra.rahi05@gmail.com}\\
   & Mobile: +91-706843851\\
  \href{https://linkedin.com/in/trivendra-rahi}{LinkedIn: linkedin.com/in/trivendra-rahi} & \\








\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IIT Guwahati}{Guwahati, Assam}
      {MTECH in Mechanical Engineering}{2020-2022}
    \resumeSubheading
      {Shri G.S. Institute of Science and Technology}{Indore, M.P.}
      {BTECH in Mechanical Engineering}{2016-2020}
  \resumeSubHeadingListEnd


\section{Skills Summary}
 \resumeSubHeadingListStart
 \resumeSubItem{Machine Learning}{TensorFlow, Keras, Scikit-learn, Neural Networks, Predictive Analytics}
 \resumeSubItem{Data Analysis}{Statistical Data Analysis, Time Series Analysis, Data Wrangling, Data Visualization}
 \resumeSubItem{Programming}{Python, SQL, R, Matlab}
 \resumeSubItem{Tools}{Pandas, Numpy, Excel, Dataiku, Github, JMP, Plotly, Spotfire, OpenCV}
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{~~Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GE Aerospace}{Bengaluru, India}
      {Senior Data Scientist | Fleet Analytics}{July 2024 - Present}
      \resumeItemListStart
        \resumeItem{Machine Learning Model Development}{Led end-to-end development of machine learning models to predict hardware conditions, from problem definition to industrial deployment.}
        \resumeItem{Stakeholder Collaboration}{Collaborated with stakeholders to align analytics with business goals, define success criteria, and identify data requirements.}
        \resumeItem{Data Analysis and Preprocessing}{Conducted data preprocessing, validation, and exploratory analysis to identify key predictors and ensure data quality.}
        \resumeItem{Model Deployment}{Designed, trained, and deployed robust machine learning models, achieving a 15\% increase in success criteria for a key analytics project under my leadership.}
      \resumeItemListEnd

    \resumeSubheading
      {GE Aerospace}{Bengaluru, India}
      {Edison Engineer | Image Analytics}{January 2024 - July 2024}
      \resumeItemListStart
        \resumeItem{CNN Architecture Optimization}{Developed and optimized CNN architectures (VGG16, InceptionNet, ResNet, UNet) using TensorFlow for image classification and segmentation.}
        \resumeItem{Model Training Pipeline}{Delivered a new model training and inference pipeline using Keras, improving model development time by 30\%.}
        \resumeItem{Image Processing}{Utilized OpenCV for advanced image processing tasks.}
        \resumeItem{Aerospace Applications}{Contributed to robust image analytics models for aerospace applications.}
      \resumeItemListEnd

    \resumeSubheading
      {GE Aerospace}{Bengaluru, India}
      {Edison Engineer | Fleet Analytics}{August 2022 - December 2023}
      \resumeItemListStart
        \resumeItem{Analytics Pipeline Development}{Developed a full analytics pipeline for the Long Haul Analytics team, addressing a new use case from problem definition to model deployment.}
        \resumeItem{Maintenance Cost Reduction}{Designed and implemented machine learning models that reduced maintenance costs by 15\%.}
        \resumeItem{Cross-functional Collaboration}{Collaborated with cross-functional teams to ensure successful deployment and adoption of the solution.}
        \resumeItem{Physics-Based Modeling}{Improved physics-based modeling, leading to a significant reduction in maintenance burden for airline customers.}
        \resumeItem{Outlier Detection}{Developed standard method of outlier detection and removal and presented in the interval board to set it as standard process for all other analytics.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------------
\section{~~Certifications}
\resumeSubHeadingListStart
    \resumeSubItem{Google}{Foundation: Data, Data, Everywhere}
    \resumeSubItem{Google}{Ask Questions to Make Data-Driven Decisions}
    \resumeSubItem{DeepLearning.AI}{Neural Network and Deep Learning}
    \resumeSubItem{DeepLearning.AI}{Convolutional Neural Network}
    \resumeSubItem{Udemy}{Python for Data Science and Machine Learning Bootcamp}
    \resumeSubItem{Udemy}{100 Days of Code – The Complete Python Pro Bootcamp}
\resumeSubHeadingListEnd

%-----------Activities and Interests-----------------
\section{~~Activities and Interests}
\resumeSubHeadingListStart
    \resumeSubItem{}{Chess, Video Games, Table Tennis, Traveling, Documentaries}
\resumeSubHeadingListEnd



\end{document}